---
title: "Survivorship Analysis"
author: "John Parsons"
date: "5/17/2020"
output: html_document
---

# Load Required Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("broom")
library(tidyverse) #ggplot
library(dplyr) #data transformation
library(readr)
library(lubridate) #date manipulation
library(ggpubr)
library(car)
library(RColorBrewer) #plot colors
library(MuMIn) #model.sel, dredge
library(glmmTMB) #GLMMs
#library(jtools) #model analysis
library(sjPlot) #model output table
library(DHARMa) #model diagnostics
library(glmmADMB) #alternate package for GLMM - interested in using MCMC
library(broom)
```

# Data Tidying/Transformations
```{r}
#read in data
june18_dat <- read.csv("data_raw/SeedlingTransectDataRawSummer18.csv", header = TRUE, na.strings = "")
str(june18_dat)

#remove blank rows and columns
june18_dat <- june18_dat %>% 
  dplyr::select(-17, -18, -19) %>% 
  slice(3:nrow(june18_dat))

#move first row to column names and remove first row
colnames(june18_dat) <- as.matrix(june18_dat[1,])
june18_dat <- slice(june18_dat, 2:nrow(june18_dat))

#fill out all rows of first three columns
june18_dat <- fill(june18_dat, 1:3, .direction = "down")

#fix names
june18_dat <- june18_dat %>% 
  dplyr::rename(seedlings = 8,
                after_1st_yr = 9,
                old_seedlings = 10,
                alive_dess = 13,
                dead_dess = 14,
                herb_above = 15,
                herb_below = 16)

june18_dat$Site <- dplyr::recode(june18_dat$Site, "Intermediate " = "Intermediate", "Mesic " = "Mesic")
june18_dat$Plot <- dplyr::recode(june18_dat$Plot, "1" = "O", "2" = "W", "3" = "WC")

june18_dat$seedlings <- as.numeric(as.character(june18_dat$seedlings))

#convert factors to numeric
june18_dat <- june18_dat %>% 
  mutate_at(c("seedlings", "after_1st_yr", "old_seedlings", "dead", "clump", "alive_dess", "dead_dess", "herb_above", "herb_below"), as.character) %>% 
  mutate_at(c("seedlings", "after_1st_yr", "old_seedlings", "dead", "clump", "alive_dess", "dead_dess", "herb_above", "herb_below"), as.numeric)

#replace na's with 0's
june18_dat[is.na(june18_dat)] <- 0

#new column for clump presence/absence
june18_dat <- june18_dat %>% 
  mutate(clump_YN = if_else(clump == 0, 0, 1))
#june18_dat$clump_YN <- as.factor(june18_dat$clump_YN)

#new column for large herbivore presence (W or WC)
june18_dat <- june18_dat %>% 
  mutate(grazed_YN = if_else(Plot == "O", 0, 1))
june18_dat$grazed_YN <- as.factor(june18_dat$grazed_YN)

#new columns for total seedlings, alive seedlings and proportion dead
june18_dat <- june18_dat %>% 
  mutate(total = seedlings + after_1st_yr + old_seedlings) %>% 
  mutate(alive = total - dead) %>% 
  mutate(prop_dead = (dead/total))

#new columns for aboveground, belowground, and overall herbivory presence
june18_dat <- june18_dat %>% 
  mutate(above_YN = if_else(herb_above == 0, 0, 1)) %>%
  mutate(below_YN = if_else(herb_below == 0, 0, 1)) %>% 
  mutate(herb_YN = if_else(above_YN == 1, 1, if_else(below_YN == 1, 1, 0))) 

#write tidy data to .csv
june18_tidy.csv <- write.csv(june_18_dat, "data/june18_tidy.csv", row.names = FALSE)
```

# Analyses and Visualizations

## Total Seedling Abundance

### Exploratory Visualizations
```{r}
#these visualizations correspond to seedling establishment (includes both alive and dead seedlings)
#see next chunk for visualizations of living seedlings only (seedling survival)

ggplot(june18_dat, aes(x = total))+
  geom_histogram(binwidth = 1)

ggplot(june18_dat, aes(x = total)) +
  stat_ecdf(geom = "step")

#total seedling abundance by site and plot:
june18_plot <- june18_dat %>% 
  dplyr::group_by(Site, Plot) %>% 
  dplyr::summarize(mean = list(mean_se(total))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = Plot)) +
    geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
    geom_errorbar(aes(ymax = ymax, ymin = ymin),
                  position = position_dodge(width = 0.9),
                  width = 0.2) +
    labs(x = "Climate Site", 
         y = "Average Number of Seedlings per Transect", 
         title = "Number of Seedlings by Climate Site and Grazing Treatment", 
         fill = "Grazing Treatment")
june18_plot
ggsave("plots/june18_plot.png", width = 10, height = 7)

#save settings for other charts
bar_plot <- geom_bar(stat = "identity", position = position_dodge(width = 0.9))
error_bars <- geom_errorbar(aes(ymax = ymax, ymin = ymin),
                                position = position_dodge(width = 0.9),
                                width = 0.2)

#same plot as above but as dotplot:
june18_dotplot <- june18_dat %>% 
  dplyr::group_by(Site, Plot) %>% 
  dplyr::summarize(mean = list(mean_se(total))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, color = Plot)) +
    geom_point(size = 1.5) +
    geom_path(aes(group = Plot), linetype = 2) +
    geom_errorbar(aes(ymax = ymax, ymin = ymin), width = 0.1) +
    labs(x = "Climate Site", 
         y = "Average Number of Seedlings per Transect", 
         title = "Number of Seedlings by Climate Site and Grazing Treatment", 
         fill = "Grazing Treatment")
june18_dotplot

#grouped by grazed Y/N instead of plot:
june18_dat %>% 
  dplyr::group_by(Site, grazed_YN) %>% 
  dplyr::summarize(mean = list(mean_se(total))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = grazed_YN)) +
    bar_plot +
    error_bars +
    labs(x = "Climate Site", 
         y = "Average Number of Seedlings per Transect", 
         title = "Number of Seedlings by Climate Site and Grazing Treatment", 
         fill = "Grazing Treatment")

#grouped by plot only:
june18_dat %>% 
  dplyr::group_by(Plot) %>% 
  dplyr::summarize(mean = list(mean_se(total))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Plot, y = y)) +
    bar_plot +
    error_bars
#cattle = fewer seedlings

#grouped by site only:
june18_dat %>% 
  dplyr::group_by(Site) %>% 
  dplyr::summarize(mean = list(mean_se(total))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y)) +
    bar_plot +
    error_bars
#Arid and Mesic roughly the same, Interm has 50% more

ggplot(june18_dat, aes(x = Site, y = total, fill = Plot)) +
  geom_boxplot()
```

### Modelling Total Seedling Abundance
```{r}
#determine best family
total_mod1 <- glmmTMB(total ~ Site*Plot + (1|Block/Transecs), data = june18_dat, family = gaussian)
total_mod2 <- glmmTMB(total ~ Site*Plot + (1|Block/Transect), data = june18_dat, family = poisson)

model.sel(list(total_mod1, total_mod2))
#gaussian is better fit

#testing other pois distributions to handle underdispersion:
total_mod2.1 <- glmmTMB(total ~ Site*Plot + (1|Block/Transect), data = june18_dat, family = genpois)
#total_mod2.2 <- glmmTMB(total ~ Site*Plot + (1|Block/Transect), data = june18_dat, family = compois)
#not working
model.sel(list(total_mod2, total_mod2.1))
#generalized poisson is better fit

#does ZI improve fit?
total_mod3 <- glmmTMB(total ~ Site*Plot + (1|Block/Transect), data = june18_dat, family = genpois, ziformula = ~1)

model.sel(list(total_mod2.1, total_mod3))
#non-ZI is better fit, but delta is small - moving to test different ZI formulas:

total_mod3.1 <- glmmTMB(total ~ Site*Plot + (1|Block/Transect), data = june18_dat, family = genpois, ziformula = ~(1|Block/Transect)) 
total_mod3.2 <- glmmTMB(total ~ Site*Plot + (1|Block/Transect), data = june18_dat, family = genpois, ziformula = ~(1|Block))
total_mod3.3 <- glmmTMB(total ~ Site*Plot + (1|Block/Transect), data = june18_dat, family = genpois, ziformula = ~(1|Site))
total_mod3.4 <- glmmTMB(total ~ Site*Plot + (1|Block/Transect), data = june18_dat, family = genpois, ziformula = ~(1|Plot))
#all above models have convergence issues

model.sel(list(total_mod2.1, total_mod3, total_mod3.1, 
               total_mod3.2, total_mod3.3, total_mod3.4))
#non-ZI and ZI = ~1 are best

#do random effects improve fit?
total_mod4 <- glmmTMB(total ~ Site*Plot, data = june18_dat, family = genpois)

model.sel(list(total_mod2.1, total_mod4))
#random effects improve fit

#which fixed effects improve fit?
total_mod5 <- glmmTMB(total ~ Site + Plot + (1|Block/Transect), data = june18_dat, family = genpois)
total_mod6 <- glmmTMB(total ~ Site + (1|Block/Transect), data = june18_dat, family = genpois)
total_mod7 <- glmmTMB(total ~ Plot + (1|Block/Transect), data = june18_dat, family = genpois)
total_mod_null <- glmmTMB(total ~ (1|Block/Transect), data = june18_dat, family = genpois)

model.sel(list(total_mod2.1, total_mod5, total_mod6, total_mod7, total_mod_null))

#full model without interaction has better fit (weight = 0.659), should I average the two models?

#testing random slopes
#total_mod8 <- glmmTMB(total ~ Site*Plot + (1 + Site|Block/Transect), data = june18_dat, family = genpois)
#fails to converge
#total_mod9 <- glmmTMB(total ~ Site*Plot + (1 + Site|Block), data = june18_dat, family = genpois)
#fails to converge
#total_mod10 <- glmmTMB(total ~ Site*Plot + (Plot|Block/Transect), data = june18_dat, family = genpois)
#fails to converge
#total_mod11 <- glmmTMB(total ~ Site*Plot + (Plot|Block), data = june18_dat, family = genpois)
#singular convergence

#no random slope models available w/out further troubleshooting

#importance of Plot
model.sel(list(total_mod5, total_mod6))
#delta AIC = 22.9
anova(total_mod5, total_mod6)
#p < 0.001

#importance of Site
model.sel(list(total_mod5, total_mod7))
#delta AIC = 41.57
#Site explains more variation than Plot?
anova(total_mod5, total_mod7)
#p < 0.001

#importance of interaction
model.sel(list(total_mod2.1, total_mod5))
#delta AIC = 1.31
#NO INTERACTION MODEL IS BETTER
anova(total_mod2.1, total_mod5)
#p = 0.1461 (not a sig diff between P+S and P*S)

#Site and Plot improve model fit, interaction is slightly worse than no interaction

#full model with generalized poisson distribution and WITHOUT interaction is best (may want to average the two models):
total_mod <- total_mod5
summary(total_mod)

#DHARMa Diagnostics:

simulationOutput <- simulateResiduals(fittedModel = total_mod, plot = T, n = 1000)
hist(simulationOutput)

testResiduals(simulationOutput, plot = T)
#uniformity, dispersion, and outlier tests all significant
#looks to be underdispersed based on QQ

testZeroInflation(simulationOutput)

tab_model(total_mod)
#tidy(total_mod)
#No tidy method for objects of class glmmTMB
```

### Trying glmmADMB on total seedling data
```{r}
total_admb1 <- glmmadmb(total ~ Site * Plot + (1|Block/Transect), data = june18_dat, family = "poisson")
total_admb2 <- glmmadmb(total ~ Site * Plot + (1|Block/Transect), data = june18_dat, family = "nbinom")
total_admb3 <- glmmadmb(total ~ Site * Plot + (1|Block/Transect), data = june18_dat, family = "poisson", zeroInflation = T)

#really slow
```

### Two-way ANOVA, total seedlings
```{r}
shapiro.test(june18_dat$total)
#non-normal

table(june18_dat$Site, june18_dat$Plot)

aov1 <- aov(seedlings ~ Plot * Site, data = june18_dat)
summary(aov1)
#looks like both Plot and Site have significant effect, and their interaction

TukeyHSD(aov1)
plot(aov1, 1)
leveneTest(seedlings ~ Plot * Site, data = june18_dat)
#non-homogenous variance
plot(aov1, 2)
#definitely not normal
```
## Living Seedling Abundance

### Exploratory Visualizations
```{r}
#these visualizations correspond to seedling survival

ggplot(june18_dat, aes(x = alive))+
  geom_histogram(binwidth = 1)

ggplot(june18_dat, aes(x = alive)) +
  stat_ecdf(geom = "step")

#living seedling abundance by site and plot:
june18_alive_plot <- june18_dat %>% 
  dplyr::group_by(Site, Plot) %>% 
  dplyr::summarize(mean = list(mean_se(alive))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = Plot)) +
    geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
    geom_errorbar(aes(ymax = ymax, ymin = ymin),
                  position = position_dodge(width = 0.9),
                  width = 0.2) +
    labs(x = "Climate Site", 
         y = "Average Number of Living Seedlings per Transect", 
         title = "Number of Living Seedlings by Climate Site and Grazing Treatment", 
         fill = "Grazing Treatment")
june18_alive_plot
ggsave("plots/june18_alive_plot.png", width = 10)

#grouped by grazed Y/N instead of plot:
june18_dat %>% 
  dplyr::group_by(Site, grazed_YN) %>% 
  dplyr::summarize(mean = list(mean_se(alive))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = grazed_YN)) +
    bar_plot +
    error_bars +
    labs(x = "Climate Site", 
         y = "Average Number of Seedlings per Transect", 
         title = "Number of Seedlings by Climate Site and Grazing Treatment", 
         fill = "Grazing Treatment" )

#grouped by plot only:
june18_dat %>% 
  dplyr::group_by(Plot) %>% 
  dplyr::summarize(mean = list(mean_se(alive))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Plot, y = y)) +
    bar_plot +
    error_bars

#grouped by site only:
june18_dat %>% 
  dplyr::group_by(Site) %>% 
  dplyr::summarize(mean = list(mean_se(alive))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y)) +
    bar_plot +
    error_bars
#all three sites are different - unlike total seedlings
#arid vs mesic affects survival, not establishment?

ggplot(june18_dat, aes(x = Site, y = alive, fill = Plot)) +
  geom_boxplot()
```

### Modeling Living Seedling Abundance
```{r}
#determine best family
alive_mod1 <- glmmTMB(alive ~ Site*Plot + (1|Block/Transect), data = june18_dat, family = gaussian)
alive_mod2 <- glmmTMB(alive ~ Site*Plot + (1|Block/Transect), data = june18_dat, family = poisson)
alive_mod3 <- glmmTMB(alive ~ Site*Plot + (1|Block/Transect), data = june18_dat, family = genpois)
#alive_mod4 <- glmmTMB(total ~ Site*Plot + (1|Block/Transect), data = june18_dat, family = compois)
#doesnt work

model.sel(list(alive_mod1, alive_mod2, alive_mod3))
#generalized poisson is best distribution

#testing ZI
alive_mod5 <- glmmTMB(alive ~ Site*Plot + (1|Block/Transect), data = june18_dat, family = genpois, ziformula = ~1)
alive_mod6 <- glmmTMB(alive ~ Site*Plot + (1|Block/Transect), data = june18_dat, family = genpois, ziformula = ~(1|Block/Transect))
#NA function eval/convergence problem
alive_mod7 <- glmmTMB(alive ~ Site*Plot + (1|Block/Transect), data = june18_dat, family = genpois, ziformula = ~(1|Block))
#convergence problem

model.sel(list(alive_mod3, alive_mod5))
#non-ZI is better, delta = 2.04

#do random effects imrpove model fit?
alive_mod8 <- glmmTMB(alive ~ Site*Plot, data = june18_dat, family = genpois)

model.sel(list(alive_mod3, alive_mod8))
#random effects do improve fit

#which fixed effects improve fit?
alive_mod9 <- glmmTMB(alive ~ Site + Plot + (1|Block/Transect), data = june18_dat, family = genpois)
alive_mod10 <- glmmTMB(alive ~ Site + (1|Block/Transect), data = june18_dat, family = genpois)
alive_mod11 <- glmmTMB(alive ~ Plot + (1|Block/Transect), data = june18_dat, family = genpois)
#all above models throw NA function eval, but no convergence issues
alive_mod_null <- glmmTMB(alive ~ (1|Block/Transect), data = june18_dat, family = genpois)

model.sel(list(alive_mod3, alive_mod9, alive_mod10, alive_mod11, alive_mod_null))
#full model is best

#importance of Site
model.sel(list(alive_mod9, alive_mod11))
#delta AIC = 381.43
anova(alive_mod9, alive_mod11)
#p < 0.001

#importance of Plot
model.sel(list(alive_mod9, alive_mod10))
#delta AIC = 6.37
anova(alive_mod9, alive_mod10)
#p < 0.005

#importance of interaction
model.sel(list(alive_mod3, alive_mod9))
#delta AIC = 52.75
anova(alive_mod3, alive_mod9)
#p < 0.001

#full model with generalized poisson distribution is best fit:
alive_mod <- alive_mod3

#DHARMa Diagnostics:

alive_sim <- simulateResiduals(fittedModel = alive_mod, plot = T, n = 1000)
hist(alive_sim)

testResiduals(alive_sim, plot = T)
#uniformity, dispersion, and outlier tests all significant
#looks to be underdispersed based on QQ

testZeroInflation(alive_sim)
#looks to be ZI?

tab_model(alive_mod)
#tidy(total_mod)
#No tidy method for objects of class glmmTMB
```

### Exploratory Visualizations: Clumps
```{r}
ggplot(june18_dat, aes(x = clump))+
  geom_histogram()
#mostly zero or one

ggplot(june18_dat, aes(x = clump_YN))+
  geom_histogram(stat = "count")
 
#clump presence by site and plot
june18_clump_plot <- june18_dat %>% 
  dplyr::group_by(Site, Plot) %>% 
  dplyr::summarize(mean = list(mean_se(clump_YN))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = Plot)) +
    bar_plot +
    error_bars +
    labs(x = "Climate Site", 
         y = "Proportion of Transects with Clumps", 
         title = "Presence of Clumps by Climate Site and Grazing Treatment", 
         fill = "Grazing Treatment")
june18_clump_plot
ggsave("plots/june18_clump_plot.png", width = 10)
```

### Two-way ANOVA, clumps
```{r}
shapiro.test(june18_dat$clump_YN)
#non-normal

table(june18_dat$Site, june18_dat$grazed_YN)

aov2 <- aov(clump_YN ~ grazed_YN * Site, data = june18_dat)
summary(aov2)
#looks like both Plot and Site have significant effect, and their interaction

TukeyHSD(aov2)
#significant differences between plots and between sites

plot(aov2, 1)

leveneTest(clump_YN ~ grazed_YN * Site, data = june18_dat)
#non-homogenous variance

plot(aov2, 2)
#definitely not normal
```

### Exploratory Visualizations, seedling death
```{r}
ggplot(june18_dat, aes(x = dead)) +
  geom_histogram()

ggplot(june18_dat, aes(x = total, y = prop_dead)) + 
  geom_point() +
  geom_smooth()

ggplot(june18_dat, aes(x = Plot, y = Site, fill = dead)) +
  geom_tile()

#histogram of proportion dead
ggplot(june18_dat, aes(x = prop_dead)) +
  geom_histogram()
#very interesting - most transects are either 0 or 100% dead

#proportion dead by plot and site
june18_dat %>% 
  dplyr::group_by(Site, Plot) %>% 
  dplyr::summarize(mean = list(mean_se(prop_dead))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = Plot)) +
    bar_plot +
    error_bars +
    labs(x = "Climate Site", 
         y = "Proportion of Seedlings Dead", 
         title = "Seedling Death by Climate Site and Grazing Treatment", 
         fill = "Grazing Treatment") +
    scale_fill_brewer(palette = "Dark2")
#arid has way higher proportion of dead saplings than other climate sites

#proportion dead by site only
june18_dat %>% 
  dplyr::group_by(Site) %>% 
  dplyr::summarize(mean = list(mean_se(prop_dead))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y)) +
    bar_plot +
    error_bars

#proportion dead by plot only
june18_dat %>% 
  dplyr::group_by(Plot) %>% 
  dplyr::summarize(mean = list(mean_se(prop_dead))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Plot, y = y)) +
    bar_plot +
    error_bars
#potentially sig. dif. between O and W/WC
#O has lowest death rate - compare this to herbivory presence
```

### Modelling Proportion Dead
```{r}
june18_dat$prop_dead <- round(june18_dat$prop_dead)
june18_dat$prop_dead <- as.factor(as.numeric(june18_dat$prop_dead))

#best binomial link?
dead_mod1 <- glmmTMB(prop_dead ~ Site*Plot + (1|Block/Transect), data = june18_dat, family = "binomial")
dead_mod_probit <- glmmTMB(prop_dead ~ Site*Plot + (1|Block/Transect), data = june18_dat, family = binomial(link = "probit"))

mods <- list(dead_mod1, dead_mod_probit)
model.sel(mods)
#logit is better

#does ZI improve fit?
dead_mod2 <- glmmTMB(prop_dead ~ Site*Plot + (1|Block/Transect), data = june18_dat, family = "binomial", ziformula = ~1)

mods <- list(dead_mod1, dead_mod2)
model.sel(mods)
#non-ZI is better fit

#do random effects improve fit?
dead_mod3 <- glmmTMB(prop_dead ~ Site*Plot, data = june18_dat, family = "binomial")

mods <- list(dead_mod1, dead_mod3)
model.sel(mods)
#random effects improve fit

#which fixed effects improve fit?
dead_mod4 <- glmmTMB(prop_dead ~ Site + Plot + (1|Block/Transect), data = june18_dat, family = "binomial")
dead_mod5 <- glmmTMB(prop_dead ~ Site + (1|Block/Transect), data = june18_dat, family = "binomial")
dead_mod6 <- glmmTMB(prop_dead ~ Plot + (1|Block/Transect), data = june18_dat, family = "binomial")
dead_mod_null <- glmmTMB(prop_dead ~ (1|Block/Transect), data = june18_dat, family = "binomial")

mods <- list(dead_mod1, dead_mod4, dead_mod5, dead_mod6, dead_mod_null)
model.sel(mods)
#full model w/interaction has best fit

#testing random slopes
#dead_mod7 <- glmmTMB(prop_dead ~ Site*Plot + (1 + Site|Block/Transect), data = june18_dat, family = "binomial")
#fails to converge
#dead_mod7 <- glmmTMB(prop_dead ~ Site*Plot + (1 + Site|Block), data = june18_dat, family = "binomial")
#fails to converge
#dead_mod8 <- glmmTMB(prop_dead ~ Site*Plot + (Plot|Block/Transect), data = june18_dat, family = "binomial")
#fails to converge
#dead_mod8 <- glmmTMB(prop_dead ~ Site*Plot + (Plot|Block), data = june18_dat, family = "binomial")
#fails to converge

#no random slope models available

#importance of Plot
mods <- list(dead_mod4, dead_mod5)
model.sel(mods)
#delta AIC = 13.83
anova(dead_mod4, dead_mod5)
#p < 0.001

#importance of Site
mods <- list(dead_mod4, dead_mod6)
model.sel(mods)
#delta AIC = 774.56
anova(dead_mod4, dead_mod6)
#p < 0.001

#importance of interaction
mods <- list(dead_mod1, dead_mod4)
model.sel(mods)
#delta AIC = 4.66
anova(dead_mod1, dead_mod4)
#p < 0.05

#Site, Plot, and their interaction all improve model fit

#best model is full model with interaction:
dead_mod <- dead_mod1
summary(dead_mod)

#DHARMa Diagnostics:

simulationOutput <- simulateResiduals(fittedModel = dead_mod, plot = F, n = 1000)
hist(simulationOutput)

testResiduals(simulationOutput, plot = T)
#uniformity and dispersion OK, outlier test significant

tab_model(dead_mod)
#this is really ugly - I want something like Perea et al.
```

### Exploratory Visualizations, Herbivory Occurence
```{r}
ggplot(june18_dat, aes(x = herb_above)) +
  geom_histogram()

ggplot(june18_dat, aes(x = herb_below)) +
  geom_histogram()

#switching to occurrence of any herbivory
ggplot(june18_dat, aes(x = herb_YN)) +
  geom_histogram(binwidth = 1)

#occurrence of herbivory by plot and site:
june18_dat %>% 
  dplyr::group_by(Site, Plot) %>% 
  dplyr::summarize(mean = list(mean_se(herb_YN))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = Plot)) +
    bar_plot +
    error_bars +
    labs(x = "Climate Site", 
         y = "Herbivory Occurence, % of Total Seedlings", 
         title = "Herbivory by Climate Site and Grazing Treatment", 
         fill = "Grazing Treatment") +
    scale_fill_brewer(palette = "Dark2")
#weird interaction between plot WC and site Mesic, see model table as well

#total herbivory by site only
june18_dat %>% 
  dplyr::group_by(Site) %>% 
  dplyr::summarize(mean = list(mean_se(herb_YN))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y)) +
    bar_plot +
    error_bars
#Arid has way more herbivory - confirms suggestion by L-S

#herbivory by site, split into above- and below- ground
june18_dat %>% 
  gather(herb_type, herb, above_YN:below_YN) %>% 
  dplyr::group_by(Site, herb_type) %>% 
  dplyr::summarize(mean = list(mean_se(herb))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = herb_type)) +
    geom_bar(stat = "identity", position = "stack")
#Arid dominated by below-ground, Mesic and Interm by above-ground

#total herbivory by plot only
june18_dat %>% 
  dplyr::group_by(Plot) %>% 
  dplyr::summarize(mean = list(mean_se(herb_YN))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Plot, y = y)) +
    bar_plot +
    error_bars
#TOTAL herbivory increases with grazing guilds present

#herbivory by plot, split between above- and below- ground
june18_dat %>% 
  gather(herb_type, herb, above_YN:below_YN) %>% 
  dplyr::group_by(Plot, herb_type) %>% 
  dplyr::summarize(mean = list(mean_se(herb))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Plot, y = y, fill = herb_type)) +
    geom_bar(stat = "identity", position = "stack")
#aboveground herbivory roughly the same in O and W, much more in WC
```
### Modeling Herbivory Occurrence
```{r}
#test links
herb_mod1 <- glmmTMB(herb_YN ~ Plot*Site + (1|Block/Transect), data = june18_dat, family = "binomial")
herb_mod2 <- glmmTMB(herb_YN ~ Plot*Site + (1|Block/Transect), data = june18_dat, family = binomial(link = "probit"))

model.sel(list(herb_mod1, herb_mod2))
#logit is better, but delta is only 0.31...

#test ZI
herb_mod3 <- glmmTMB(herb_YN ~ Plot*Site + (1|Block/Transect), data = june18_dat, family = "binomial", ziformula = ~1)

model.sel(list(herb_mod1, herb_mod3))
#might want to include ZI, delta is only 1.37...

#test ranef
herb_mod4 <- glmmTMB(herb_YN ~ Plot*Site, data = june18_dat, family = "binomial")

model.sel(list(herb_mod1, herb_mod4))
#random effects improve fit

#test fixed effects
herb_mod5 <- glmmTMB(herb_YN ~ Plot + Site + (1|Block/Transect), data = june18_dat, family = "binomial")
herb_mod6 <- glmmTMB(herb_YN ~ Plot + (1|Block/Transect), data = june18_dat, family = "binomial")
herb_mod7 <- glmmTMB(herb_YN ~ Site + (1|Block/Transect), data = june18_dat, family = "binomial")
herb_mod_null <- glmmTMB(herb_YN ~ (1|Block/Transect), data = june18_dat, family = "binomial")

model.sel(list(herb_mod1, herb_mod5, herb_mod6, herb_mod7, herb_mod_null))
#full model w/ interaction is best

#importance of Plot
model.sel(list(herb_mod5, herb_mod7))
#delta AIC = 15.08
anova(herb_mod5, herb_mod7)
#p < 0.001

#importance of Site
model.sel(list(herb_mod5, herb_mod6))
#delta AIC = 197.04
anova(herb_mod5, herb_mod6)
#p < 0.001

#importance of interaction
model.sel(list(herb_mod1, herb_mod5))
#delta AIC = 48.76
anova(herb_mod1, herb_mod5)
#p < 0.001

#Site, Plot, and their interaction all improve model fit
#best model is full model:
herb_mod <- herb_mod1
summary(herb_mod)

#DHARMa Diagnostics:
simulationOutput <- simulateResiduals(fittedModel = herb_mod, plot = F, n = 1000)
hist(simulationOutput)
testResiduals(simulationOutput, plot = T)
#uniformity dispersion and outliers OK

#model results table:
tab_model(herb_mod)
```

### Comparing herbivory to death
```{r}
june18_dat$herb_YN <- as.factor(as.character(june18_dat$herb_YN))

june18_dat %>%
  dplyr::group_by(herb_YN) %>% 
  dplyr::summarize(mean = list(mean_se(prop_dead))) %>%
  unnest(mean) %>%
  ggplot(aes(x = herb_YN, y = y)) +
    geom_bar(stat = "identity")
#herbivory results in much higher death rate

june18_dat %>%
  dplyr::group_by(Site, herb_YN) %>% 
  dplyr::summarize(mean = list(mean_se(prop_dead))) %>%
  unnest(mean) %>%
  ggplot(aes(x = herb_YN, y = y, fill = Site)) +
    geom_bar(stat = "identity", position = "dodge")
#effect of herbivory fairly consistent across climate sites

june18_dat %>%
  dplyr::group_by(Plot, herb_YN) %>% 
  dplyr::summarize(mean = list(mean_se(prop_dead))) %>%
  unnest(mean) %>%
  ggplot(aes(x = herb_YN, y = y, fill = Plot)) +
    geom_bar(stat = "identity", position = "dodge")
#herbivory increases death rate 4x in O and W, but only 2x in WC - herbivory by cattle not as destructive as herbivory by wildlife? Or presence of cattle somehow decreases herbivory intensity?

june18_dat %>% 
  gather(herb_type, herb, above_YN:below_YN) %>% 
  dplyr::group_by(herb_type, herb) %>% 
  dplyr::summarize(mean = list(mean_se(prop_dead))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = herb_type, y = herb, fill = y)) +
    geom_tile()
#complex interaction - aboveground herbivory decreases death rate, belowground herbiory increases it
```

### Adding herbivory to proportion dead model
```{r}
dead_mod7 <- glmmTMB(prop_dead ~ Plot*Site + herb_YN + (1|Block/Transect), data = june18_dat, family = "binomial")

model.sel(list(dead_mod, dead_mod7))
#adding herbivory improves fit

dead_mod8 <- glmmTMB(prop_dead ~ herb_YN + (1|Block/Transect), data = june18_dat, family = "binomial")

model.sel(list(dead_mod, dead_mod8))
```