---
title: "Seedling Analysis"
author: "John Parsons"
date: "6/22/2020"
output:
  html_document: default
  pdf_document: default
---

### Load Required Packages
```{r}
#install.packages("webshot")
library(tidyverse) #ggplot
library(dplyr) #data transformation
group_by <- dplyr::group_by
summarize <- dplyr::summarise
select <- dplyr::select
recode <- dplyr::recode
rename <- dplyr::rename
library(readr)
library(lubridate) #date manipulation
library(ggpubr)
library(car)
library(RColorBrewer) #plot colors
library(MuMIn) #model.sel, dredge
library(glmmTMB) #GLMMs
#library(jtools) #model analysis
library(sjPlot) #model output table
library(DHARMa) #model diagnostics
library(effects)
library(emmeans) #effects testing
library(installr)
library(sjstats)
#install.pandoc()
library(gt)
remotes::install_github("rstudio/gt")
library(webshot)
webshot::install_phantomjs() #saving gt tables
```

### Data Tidying/Transformations
```{r include=FALSE}
#read in data
june18_dat <- read.csv("data_raw/SeedlingTransectDataRawSummer18.csv", header = TRUE, na.strings = "")
str(june18_dat)
#View(june18_dat)

#remove blank rows and columns
june18_dat <- june18_dat %>% 
  select(-17, -18, -19) %>% 
  slice(3:nrow(june18_dat))

#move first row to column names and remove first row
colnames(june18_dat) <- as.matrix(june18_dat[1,])
june18_dat <- slice(june18_dat, 2:nrow(june18_dat))

#get rid of unused levels
june18_dat <- droplevels(june18_dat)
june18_dat$Site <- recode(june18_dat$Site, "Intermediate " = "Intermediate", "Mesic " = "Mesic")
june18_dat$Plot <- recode(june18_dat$Plot, "1" = "O", "2" = "W", "3" = "WC")

#fill out all rows of first three columns
june18_dat <- fill(june18_dat, 1:3, .direction = "down")

#fix names
june18_dat <- june18_dat %>% 
  rename(seedlings = 8,
                after_1st_yr = 9,
                old_seedlings = 10,
                alive_dess = 13,
                dead_dess = 14,
                herb_above = 15,
                herb_below = 16)

#convert factors to numeric
june18_dat <- june18_dat %>% 
  mutate_at(c("seedlings", "after_1st_yr", "old_seedlings", "dead", "clump", "alive_dess", "dead_dess", "herb_above", "herb_below"), as.character) %>% 
  mutate_at(c("seedlings", "after_1st_yr", "old_seedlings", "dead", "clump", "alive_dess", "dead_dess", "herb_above", "herb_below"), as.numeric)

#replace na's with 0's
june18_dat[is.na(june18_dat)] <- 0

#sum across transects
june18_dat <- june18_dat %>% 
  dplyr::group_by(Year, Month, Site, Block, Plot) %>% 
  summarise(seedlings = sum(seedlings), after_1st_yr = sum(after_1st_yr), old_seedlings = sum(old_seedlings), dead = sum(dead), clump = sum(clump), alive_dess = sum(alive_dess), dead_dess = sum(dead_dess), herb_above = sum(herb_above), herb_below = sum(herb_below))

#add Random Effect ID for block within site (replaced with Site/Block)
june18_dat <- june18_dat %>% 
  mutate(RE = paste(Site, Block, sep = "_"))
june18_dat$RE <- as.factor(june18_dat$RE)

#new column for clump presence/absence
june18_dat <- june18_dat %>% 
  mutate(clump_YN = if_else(clump == 0, 0, 1))
june18_dat$clump_YN <- as.factor(june18_dat$clump_YN)

#new column for large herbivore presence (W or WC)
june18_dat <- june18_dat %>% 
  mutate(grazed_YN = if_else(Plot == "O", 0, 1))
june18_dat$grazed_YN <- as.factor(june18_dat$grazed_YN)

#new columns for total seedlings, alive seedlings and proportion dead
june18_dat <- june18_dat %>% 
  mutate(total = seedlings + after_1st_yr + old_seedlings) %>% 
  mutate(alive = total - dead) %>% 
  mutate(prop_dead = (dead/total))

#new column for dessication occurrence
june18_dat <- june18_dat %>% 
  mutate(dess_YN = if_else(alive_dess != 0, 1, if_else(dead_dess != 0, 1, 0)))

#new columns for above-ground, below-ground, and overall herbivory occurrence, and for proportion of seedlings with above- or below-ground herbivory
june18_dat <- june18_dat %>% 
  mutate(above_YN = if_else(herb_above == 0, 0, 1)) %>%
  mutate(below_YN = if_else(herb_below == 0, 0, 1)) %>% 
  mutate(both_herb = if_else((herb_below == 1 | herb_above == 1), 1, 0)) %>% 
  mutate(herb_YN = if_else(above_YN == 1, 1, if_else(below_YN == 1, 1, 0))) %>% 
  mutate(above_prop = herb_above/total) %>% 
  mutate(below_prop = herb_below/total)
june18_dat$above_YN <- as.factor(june18_dat$above_YN)
june18_dat$below_YN <- as.factor(june18_dat$below_YN)
june18_dat$both_herb <- as.factor(june18_dat$both_herb)
june18_dat$herb_YN <- as.factor(june18_dat$herb_YN)

#write tidy data to .csv
june18_sum_tidy <- write.csv(june18_dat, "data/june18_sum.csv", row.names = FALSE)
```

# Analyses and Visualizations

## Total Seedling Abundance

### Exploratory Visualizations
```{r echo=FALSE}
ggplot(june18_dat, aes(x = total))+
  geom_histogram(binwidth = 10)

ggplot(june18_dat, aes(x = total)) +
  stat_ecdf(geom = "step")
```

* these visualizations correspond to seedling establishment (includes both alive and dead seedlings)
* see next section for visualizations of living seedlings only (seedling survival)

Total seedling abundance by site and plot:
```{r echo=FALSE}
total_plot <- june18_dat %>% 
  dplyr::group_by(Site, Plot) %>% 
  dplyr::summarize(mean = list(mean_se(total))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = Plot)) +
    geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
    geom_errorbar(aes(ymax = ymax, ymin = ymin),
                  position = position_dodge(width = 0.9),
                  width = 0.2) +
    labs(x = "Climate Site", 
         y = "Average Number of Seedlings per Plot", 
         title = "Number of Seedlings by Climate Site and Grazing Treatment", 
         fill = "Grazing Treatment") +
    scale_fill_brewer(palette = "Dark2")
total_plot
ggsave("plots/total_plot.png", width = 10, height = 7)
```


save settings for other charts
```{r include=FALSE}
bar_plot <- geom_bar(stat = "identity", position = position_dodge(width = 0.9))
error_bars <- geom_errorbar(aes(ymax = ymax, ymin = ymin),
                                position = position_dodge(width = 0.9),
                                width = 0.2)
```

Grouped by grazed Y/N instead of plot:
```{r echo=FALSE}
june18_dat %>% 
  dplyr::group_by(Site, grazed_YN) %>% 
  dplyr::summarize(mean = list(mean_se(total))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = grazed_YN)) +
    bar_plot +
    error_bars +
    labs(x = "Climate Site", 
         y = "Average Number of Seedlings per Plot", 
         title = "Number of Seedlings by Climate Site and Grazing Treatment", 
         fill = "Grazing Treatment")
```

Grouped by plot only:
```{r echo=FALSE}
june18_dat %>% 
  dplyr::group_by(Plot) %>% 
  dplyr::summarize(mean = list(mean_se(total))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Plot, y = y)) +
    bar_plot +
    error_bars +
  labs(y = "average seedlings per Plot")
```

* more herbivores = fewer seedlings

Grouped by site only:
```{r echo=FALSE}
june18_dat %>% 
  dplyr::group_by(Site) %>% 
  dplyr::summarize(mean = list(mean_se(total))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y)) +
    bar_plot +
    error_bars +
  labs(y = "average seedlings per plot")
```

* no big differences here

### Modelling Total Seedling Abundance

Optimal Fixed Effects Structure:
```{r include=FALSE}
#no zeroes in summed count data (see above)
#start with truncated poisson distribution and full model:
total_mod1 <- glmmTMB(total ~ Site*Plot + (1|Site/Block), data = june18_dat, family = truncated_poisson)

dredge(total_mod1)
#full model is best

total_mod <- total_mod1

total_table <- dredge(total_mod) %>% 
  gt() %>% 
    tab_header(title = "Model Comparison: Total Seedling Abundance") %>%
    tab_spanner(label = md("*Fixed Effects*"), columns = 3:5) %>% 
    cols_label("cond(Plot)" = md("*Treatment*"), 
               "cond(Site)" = "Climate",
               "cond(Plot:Site)" = "Treatment:Climate") %>% 
    cols_hide(columns = c(1,2,7,9)) %>% 
    fmt_number(columns = vars(AICc, delta, weight)) %>%
    fmt_missing(columns = 3:5, missing_text = "-")

gtsave(total_table, "plots/total_table.png")
```

```{r}
total_table
```

DHARMa Diagnostics:
```{r echo=FALSE}
total_sim <- simulateResiduals(fittedModel = total_mod, plot = F, n = 1000)
hist(total_sim)
testResiduals(total_sim, plot = T)
```

*uniformity, dispersion, and outlier tests all non-significant

Test other distributions (not necessary?)
```{r echo=FALSE}
fam_list <- list(family = alist(
    truncpois = truncated_poisson,
    genpois = genpois,
    poisson = poisson,
    nbinom1 = nbinom1,
    nbinom2 = nbinom2
    ))

dredge(total_mod, varying = fam_list)
#truncated poisson only marginally better than regular poisson

total_mod_pois <- update(total_mod, family = poisson)

total_pois_sim <- simulateResiduals(fittedModel = total_mod_pois, plot = F, n = 1000)
hist(total_pois_sim)
testResiduals(total_pois_sim, plot = T)
#meets assumptions well

model.sel(list(total_mod, total_mod_pois))
```
* any benefit to choosing poisson? less transformations of the data required?

Testing Effects
```{r echo=FALSE}
plot(allEffects(total_mod))

emmeans(total_mod, pairwise ~ Site)
#all non-sig
emmeans(total_mod, pairwise ~ Plot)
#all significant

emmip(total_mod, Plot ~ Site)
#subsetting by Plot:
emmeans(total_mod, pairwise ~ Site | Plot)
#all Site contrasts non-significant 

emmip(total_mod, Site ~ Plot)
#subsetting by Site:
emmeans(total_mod, pairwise ~ Plot | Site)
#all Plot contrasts significant

#r.squaredGLMM(total_mod)
#performance::r2(total_mod)
#performance::icc(total_mod)
```

* Climate, grazing treatment, and their interaction were all included as fixed effects in the model of best fit. Arid, intermediate, and mesic plots had an average of 80, 111, and 120 seedlings. There were no significant differences in seedling abundance between climates, either within each grazing treatment or when averaged across the three treatments. Across climates, exclosure plots had an average of 162 seedlings, more than both wildlife plots (93, p < 0.0001) and wildlife/cattle plots (46, p < 0.0001). Contrasts were also significant for all treatment pairs within climate sites (Table 1).

probably won't keep this chunk:
```{r eval=FALSE, include=FALSE}
#importance of Plot
model.sel(list(total_mod5, total_mod6))
#delta AIC = 22.9
anova(total_mod5, total_mod6)
#p < 0.001

#importance of Site
model.sel(list(total_mod5, total_mod7))
#delta AIC = 41.57
#Site explains more variation than Plot?
anova(total_mod5, total_mod7)
#p < 0.001

#importance of interaction
model.sel(list(total_mod2.1, total_mod5))
#delta AIC = 1.31
#NO INTERACTION MODEL IS BETTER
anova(total_mod2.1, total_mod5)
#p = 0.1461 (not a sig diff between P+S and P*S)

#Site and Plot improve model fit, interaction is slightly worse than no interaction

#full model with generalized poisson distribution and WITHOUT interaction is best (may want to average the two models):
total_mod <- total_mod5
summary(total_mod)
```

## Living Seedling Abundance

### Exploratory Visualizations
```{r}
ggplot(june18_dat, aes(x = alive))+
  geom_histogram(binwidth = 5)
#looks like negative binomial?

ggplot(june18_dat, aes(x = alive)) +
  stat_ecdf(geom = "step")
```

Living seedling abundance by site and plot:
```{r echo=FALSE}
alive_plot <- june18_dat %>% 
  dplyr::group_by(Site, Plot) %>% 
  dplyr::summarize(mean = list(mean_se(alive))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = Plot)) +
    geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
    geom_errorbar(aes(ymax = ymax, ymin = ymin),
                  position = position_dodge(width = 0.9),
                  width = 0.2) +
    labs(x = "Climate Site", 
         y = "Average Number of Living Seedlings per Plot", 
         title = "Number of Living Seedlings by Climate Site and Grazing Treatment", 
         fill = "Grazing Treatment") +
    scale_fill_brewer(palette = "Dark2")
alive_plot
ggsave("plots/alive_plot.png", width = 10)
```

Grouped by grazed Y/N instead of plot:
```{r eval=FALSE, include=FALSE}
june18_dat %>% 
  dplyr::group_by(Site, grazed_YN) %>% 
  dplyr::summarize(mean = list(mean_se(alive))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = grazed_YN)) +
    bar_plot +
    error_bars +
    labs(x = "Climate Site", 
         y = "Average Number of Living Seedlings per Plot", 
         title = "Number of Seedlings by Climate Site and Grazing Treatment", 
         fill = "Grazing Treatment" )
```

Grouped by plot only:
```{r eval=FALSE, include=FALSE}
june18_dat %>% 
  dplyr::group_by(Plot) %>% 
  dplyr::summarize(mean = list(mean_se(alive))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Plot, y = y)) +
    bar_plot +
    error_bars + 
    labs(y = "average living seedlings per plot")
```

Grouped by site only:
```{r eval=FALSE, include=FALSE}
june18_dat %>% 
  dplyr::group_by(Site) %>% 
  dplyr::summarize(mean = list(mean_se(alive))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y)) +
    bar_plot +
    error_bars + 
    labs(y = "average living seedlings per plot")
```

* all three sites are different - unlike total seedlings
* arid vs mesic affects survival, not establishment?

### Modeling Living Seedling Abundance
```{r include=FALSE}
#starting with poisson:
alive_mod1 <- glmmTMB(alive ~ Site*Plot + (1|Site/Block), 
                      data = june18_dat, family = poisson(), ziformula = ~ 0)
```

Optimal Fixed Effects and ZI Formula
```{r include=FALSE}
dredge(alive_mod1)
#Full model is best

alive_mod2 <- update(alive_mod1, ziformula = ~ 1)

model.sel(alive_mod1, alive_mod2)
#ZI ~ 1 is better than no ZI

alive_mod <- alive_mod2

alive_table <- dredge(alive_mod) %>% 
  gt() %>% 
    tab_header(title = "Model Comparison: Living Seedling Abundance") %>%
    tab_spanner(label = md("*Fixed Effects*"),
                              columns = 4:6) %>% 
    cols_label("cond(Plot)" = "Treatment", 
                             "cond(Site)" = "Climate", 
                             "cond(Plot:Site)" = "Treatment:Climate") %>% 
    cols_hide(columns = c(1:3,8,10)) %>% 
    fmt_number(columns = vars(AICc, weight)) %>%
    fmt_missing(columns = 4:6, missing_text = "-")

gtsave(alive_table, "plots/alive_table.png")
```

```{r echo=FALSE}
alive_table
```

DHARMa Diagnostics:
```{r echo=FALSE}
alive_sim <- simulateResiduals(fittedModel = alive_mod, plot = F, n = 1000)
hist(alive_sim)
testResiduals(alive_sim, plot = T)
```

*uniformity, dispersion, and outlier tests all non-significant

Testing Effects
```{r echo=FALSE}
plot(allEffects(alive_mod))

pairs(emmeans(alive_mod, "Plot"))

pairs(emmeans(alive_mod, ~ Plot | Site))

pairs(emmeans(alive_mod, "Site"))

pairs(emmeans(alive_mod, ~ Site | Plot))

#r.squaredGLMM(alive_mod)
#performance::r2(alive_mod)
#performance::icc(alive_mod)
```

Testing nbinom2
```{r eval=FALSE, include=FALSE}
alive_mod_nb <- update(alive_mod, family = nbinom2())
model.sel(list(alive_mod, alive_mod_nb))
```
* nbinom2 fits way better...

Optimal Fixed Effects and ZI Formula, nbinom2
```{r eval=FALSE, include=FALSE}
dredge(alive_mod_nb)
#Plot-only model is best

alive_mod_nb <- update(alive_mod_nb, ~ Plot + (1|Site/Block))

alive_mod_nb0 <- update(alive_mod_nb, ziformula = ~ 0)

model.sel(alive_mod_nb, alive_mod_nb0)
#ZI is better
```

DHARMa Diagnostics:
```{r eval=FALSE, include=FALSE}
alive_sim_nb <- simulateResiduals(fittedModel = alive_mod_nb, plot = F, n = 1000)
hist(alive_sim_nb)
testResiduals(alive_sim_nb, plot = T)
```
* looks fine

Testing Effects
```{r eval=FALSE, include=FALSE}
plot(allEffects(alive_mod_nb))

pairs(emmeans(alive_mod_nb, "Plot"))

#r.squaredGLMM(alive_mod)
#doesn't work with ZI

r.squaredGLMM(update(alive_mod_nb, ziformula = ~ 0))
```

* O-WC and W-WC are significant

* The best-fit model of living seedlings included grazing treatment, but not climate site. Wildlife/cattle plots had 35 living seedlings on average, less than exclosure plots (135, p < 0.005) and wildlife plots (67, p < 0.05). Exclosure and wildlife plots did not differ significantly (p = 0.3970).

old method
```{r eval=FALSE, include=FALSE}
#importance of Site
model.sel(list(alive_mod9, alive_mod11))
#delta AIC = 381.43
anova(alive_mod9, alive_mod11)
#p < 0.001

#importance of Plot
model.sel(list(alive_mod9, alive_mod10))
#delta AIC = 6.37
anova(alive_mod9, alive_mod10)
#p < 0.005

#importance of interaction
model.sel(list(alive_mod3, alive_mod9))
#delta AIC = 52.75
anova(alive_mod3, alive_mod9)
#p < 0.001
```

### Exploratory Visualizations: Clumps
```{r eval=FALSE, include=FALSE}
ggplot(june18_dat, aes(x = clump))+
  geom_histogram(binwidth = 1)

ggplot(june18_dat, aes(x = clump_YN))+
  geom_histogram(stat = "count")
```
 
Clump presence by site and plot
```{r eval=FALSE, include=FALSE}
june18_dat$clump_YN <- as.numeric(june18_dat$clump_YN)

june18_clump_plot <- june18_dat %>% 
  dplyr::group_by(Site, Plot) %>% 
  dplyr::summarize(mean = list(mean_se(clump_YN))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = (y-1), fill = Plot)) +
    bar_plot +
    labs(x = "Climate Site", 
         y = "Proportion of Plots with Clumps", 
         title = "Presence of Clumps by Climate Site and Grazing Treatment", 
         fill = "Grazing Treatment")
june18_clump_plot
ggsave("plots/june18_clump_plot.png", width = 10)
```

## Seedling Mortality

### Exploratory Visualizations

```{r echo=FALSE}
ggplot(june18_dat, aes(x = alive/total)) + 
  geom_histogram(binwidth = 0.1)
```

* lots of plots with >90% alive

Proportion dead by plot and site
```{r include=FALSE}
prop_plot <- june18_dat %>% 
              dplyr::group_by(Site, Plot) %>% 
              dplyr::summarize(mean = list(mean_se(prop_dead))) %>%
              unnest(mean) %>% 
              ggplot(aes(x = Site, y = y, fill = Plot)) +
                bar_plot +
                error_bars +
                labs(x = "Climate Site", 
                     y = "Proportion of Seedlings Dead", 
                     title = "Seedling Mortality by Climate Site and Grazing Treatment", 
                     fill = "Grazing Treatment") +
                scale_fill_brewer(palette = "Dark2")
ggsave("plots/prop_plot.png", width = 10, height = 7)
```

```{r echo=FALSE}
prop_plot
```
* arid has way higher proportion of dead seedlings than other climate sites

Proportion dead by site only
```{r eval=FALSE, include=FALSE}
june18_dat %>% 
  dplyr::group_by(Site) %>% 
  dplyr::summarize(mean = list(mean_se(prop_dead))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y)) +
    bar_plot +
    error_bars + 
    labs(y = "average proportion dead per plot")
```

Proportion dead by plot only
```{r eval=FALSE, include=FALSE}
june18_dat %>% 
  dplyr::group_by(Plot) %>% 
  dplyr::summarize(mean = list(mean_se(prop_dead))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Plot, y = y)) +
    bar_plot +
    error_bars + 
    labs(y = "average proportion dead per plot")
```

* very similar across grazing treatments

### Modelling Proportion Dead

```{r include=FALSE}
june18_dat <- june18_dat %>% mutate(no_ones = ifelse(prop_dead == 1, 0.999, prop_dead))

#start with binomial distribution 
prop_mod1 <- glmmTMB((dead/total) ~ Site + Plot + (1|Site/Block),
                     ziformula = ~ 0, data = june18_dat,
                     family = binomial(), weights = (total))
```

Optimal Fixed Effects Structure
```{r include=FALSE}
prop_mod2 <- update(prop_mod1, ~ Plot + (1|Site/Block))
prop_mod3 <- update(prop_mod1, ~ Site + (1|Site/Block))
prop_mod4 <- update(prop_mod1, ~(1|Site/Block))

model.sel(prop_mod1, prop_mod2, prop_mod3, prop_mod4)
#full model is best
```

Optimal ZI Formula?
```{r include=FALSE}
prop_modZI <- update(prop_mod1, ziformula = ~1)

model.sel(list(prop_mod1, prop_modZI))
#ZI is better

prop_mod2 <- update(prop_modZI, ~ Plot + (1|Site/Block))
prop_mod3 <- update(prop_modZI, ~ Site + (1|Site/Block))
#fails to converge
prop_mod4 <- update(prop_modZI, ~(1|Site/Block))

model.sel(prop_modZI, prop_mod2, prop_mod4)
prop_mod <- prop_modZI
```

```{r include=FALSE}
prop_table <- model.sel(prop_modZI, prop_mod2, prop_mod4) %>%
  gt() %>% 
    tab_header(title = "Model Comparison: Seedling Mortality") %>%
    tab_spanner(label = md("*Fixed Effects*"), columns = 4:5) %>% 
    cols_label("cond(Plot)" = md("*Treatment*"), "cond(Site)" = md("*Climate*")) %>% 
    cols_hide(columns = c(1,2,3,7,9)) %>% 
    fmt_number(columns = vars(AICc, weight)) %>%
    fmt_missing(columns = 4:5, missing_text = "-")

gtsave(prop_table, "plots/prop_table.png")
```

```{r echo=FALSE}
prop_table
```

DHARMa Diagnostics:
```{r echo=FALSE}
prop_dead_sim <- simulateResiduals(fittedModel = prop_mod, plot = F, n = 1000)
hist(prop_dead_sim)
testResiduals(prop_dead_sim, plot = T)
```
* uniformity, dispersion, and outlier tests all non-significant

Testing Effects
```{r echo=FALSE}
ggplot(june18_dat, aes(x = Site, y = (alive/total), fill = Plot)) +
  geom_boxplot() + 
  theme_bw()
#more variation between sites than plots, so group by site and then get pairwise contrasts between plots?

pairs(emmeans(prop_mod_ZI, "Plot"))
# O-W and O-WC are significant

pairs(emmeans(prop_mod_ZI, "Site"))
# all site contrast are significant

#r.squaredGLMM(prop_mod_ZI)
```

* The best-fit model for seedling mortality included both climate site and grazing treatment (Table 1). Arid plots had 80.15% mortality, more than both Mesic plots (0.53%, p < 0.0001) and Intermediate plots (10.43%, p < 0.001). Intermediate plots also had significantly higher mortality than Mesic plots (p < 0.05). Across climate sites, exclosure plots (33.46%) and wildlife/cattle plots (29.33%) did not significantly differ in their mortality rates (p = 0.1774). 28.32% of seedlings died in wildlife plots,  more than exclosure plots (p < 0.0005) and less than wildlife/cattle plots (p < 0.05).

## Herbivory Occurence

### Exploratory Visualizations
```{r eval=FALSE, include=FALSE}
june18_dat$herb_YN <- as.numeric(as.character(june18_dat$herb_YN))

ggplot(june18_dat, aes(x = herb_above)) +
  geom_histogram()

ggplot(june18_dat, aes(x = herb_below)) +
  geom_histogram()

#switching to occurrence of any herbivory
ggplot(june18_dat, aes(x = herb_YN)) +
  geom_histogram(stat = "count")
```

Occurrence of herbivory by plot and site
```{r echo=FALSE}
herb_plot <- june18_dat %>% 
  dplyr::group_by(Site, Plot) %>% 
  dplyr::summarize(mean = list(mean_se(herb_YN))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = Plot)) +
    bar_plot +
    error_bars +
    labs(x = "Climate Site", 
         y = "Herbivory Occurence, % of Total Seedlings", 
         title = "Herbivory by Climate Site and Grazing Treatment", 
         fill = "Grazing Treatment") +
    scale_fill_brewer(palette = "Dark2")
herb_plot
```

* weird interaction between plot WC and site Mesic

Total herbivory by site only
```{r eval=FALSE, include=FALSE}
herb_plot_site <- june18_dat %>% 
  dplyr::group_by(Site) %>% 
  dplyr::summarize(mean = list(mean_se(herb_YN))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y)) +
    bar_plot +
    error_bars +
    labs(y = "herbivory occurrence")
```

* Arid has way more herbivory - confirms suggestion by L-S

Herbivory by site, split into above- and below-ground
```{r eval=FALSE, include=FALSE}
june18_dat %>% 
  gather(herb_type, herb, above_YN:below_YN) %>% 
  dplyr::group_by(Site, herb_type) %>% 
  dplyr::summarize(mean = list(mean_se(herb))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = herb_type)) +
    geom_bar(stat = "identity", position = "stack")
```

* Arid dominated by below-ground, Mesic and Interm by above-ground

Total herbivory by plot only
```{r eval=FALSE, include=FALSE}
june18_dat %>% 
  dplyr::group_by(Plot) %>% 
  dplyr::summarize(mean = list(mean_se(herb_YN))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Plot, y = y)) +
    bar_plot +
    error_bars
```

* TOTAL herbivory increases with grazing guilds present

Herbivory by plot, split between above- and below- ground
```{r eval=FALSE, include=FALSE}
june18_dat %>% 
  gather(herb_type, herb, above_YN:below_YN) %>% 
  dplyr::group_by(Plot, herb_type) %>% 
  dplyr::summarize(mean = list(mean_se(herb))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Plot, y = y, fill = herb_type)) +
    geom_bar(stat = "identity", position = "stack")
```

* aboveground herbivory roughly the same in O and W, much more in WC


### Modeling Herbivory Occurrence
```{r eval=FALSE, include=FALSE}
#start with binomial, complimentary log-log due to asymmetric distribution:
herb_mod1 <- glmmTMB(herb_YN ~ Plot + Site + (1|Site/Block), data = june18_dat, family = binomial(link = "cloglog"))
#doesn't converge when interaction included

#test fixed effects
dredge(herb_mod1)
#site-only is best, but null model is almost as good
summary(herb_mod1)
#none of the terms are significant, further support for the null model

herb_mod <- update(herb_mod1, ~ (1|Site/Block))
summary(herb_mod)
```

DHARMa Diagnostics:
```{r eval=FALSE, include=FALSE}
herb_sim <- simulateResiduals(fittedModel = herb_mod, plot = F, n = 1000)
hist(herb_sim)
testResiduals(herb_sim, plot = T)
```

* uniformity, dispersion, and outlier tests all non-significant

Testing Effects?

old method
```{r eval=FALSE, include=FALSE}
#importance of Plot
model.sel(list(herb_mod5, herb_mod7))
#delta AIC = 15.08
anova(herb_mod5, herb_mod7)
#p < 0.001

#importance of Site
model.sel(list(herb_mod5, herb_mod6))
#delta AIC = 197.04
anova(herb_mod5, herb_mod6)
#p < 0.001

#importance of interaction
model.sel(list(herb_mod1, herb_mod5))
#delta AIC = 48.76
anova(herb_mod1, herb_mod5)
#p < 0.001
```

### Further explorations of Herbivory (work in progress)

```{r include=FALSE}
june18_dat$herb_YN <- as.factor(as.character(june18_dat$herb_YN))
```

```{r eval=FALSE, include=FALSE}
june18_dat %>%
  group_by(herb_YN) %>% 
  summarize(mean = list(mean_se(prop_dead))) %>%
  unnest(mean) %>%
  ggplot(aes(x = herb_YN, y = y)) +
    geom_bar(stat = "identity")
```
* herbivory results in much higher death rate

```{r eval=FALSE, include=FALSE}
june18_dat %>%
  group_by(Site, herb_YN) %>% 
  summarize(mean = list(mean_se(prop_dead))) %>%
  unnest(mean) %>%
  ggplot(aes(x = herb_YN, y = y, fill = Site)) +
    geom_bar(stat = "identity", position = "dodge")
```

* effect of herbivory fairly consistent across climate sites

```{r eval=FALSE, include=FALSE}
june18_dat %>%
  dplyr::group_by(Plot, herb_YN) %>% 
  dplyr::summarize(mean = list(mean_se(prop_dead))) %>%
  unnest(mean) %>%
  ggplot(aes(x = herb_YN, y = y, fill = Plot)) +
    geom_bar(stat = "identity", position = "dodge")
```

* Herbivory increases death rate in O and W, but decreases in WC - herbivory by cattle not as destructive as herbivory by wildlife? Or presence of cattle somehow decreases herbivory intensity? 
* Could be connected to what type of herbivory is occurring - as per next graph, below-ground herbivory drives death, so maybe WC plots have more above-ground herbivory and plots with no cattle have more below-ground?

Effects of different herbivory types on survival
```{r eval=FALSE, include=FALSE}
june18_dat %>% 
  gather(herb_type, herb, above_YN:herb_YN) %>% 
  group_by(herb_type, herb) %>% 
  summarize(mean = list(mean_se(prop_dead))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = herb_type, y = herb, fill = y)) +
    geom_tile()
```

* complex interaction - aboveground herbivory decreases death rate, belowground herbiory increases it
* this graph is a bit confusing - 1 and 0 on the y-axis represent whether or not the type of herbivory on the x-axis occurred, and the lighter the color, the higher proportion dead

Adding herbivory occurrence to proportion dead model
```{r eval=FALSE, include=FALSE}
prop_mod_herb <- update(prop_mod0, ~ Site + herb_YN + (1|Site/Block))

model.sel(list(prop_mod0, prop_mod_herb))
```

* adding herbivory occurence does not improve fit

Investigating frequency of herbivory types
```{r eval=FALSE, include=FALSE}
ggplot(june18_dat, aes(x=herb_above)) +
  geom_histogram(binwidth = 1)

ggplot(june18_dat, aes(x=above_prop)) +
  geom_histogram()
```

Proportion of seedlings with above-ground herbivory:
```{r echo=FALSE}
above_plot <- june18_dat %>% 
  group_by(Plot, Site) %>% 
  summarize(mean = list(mean_se(above_prop))) %>% 
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = Plot)) +
  bar_plot +
  error_bars +
  scale_fill_brewer(palette = "Dark2")
above_plot
ggsave("plots/above_plot.png", width = 10, height = 7)
```

* pretty intuitive, addition of cattle clearly increases above-ground herbivory, especially in mesic

Proportion of seedlings with below-ground herbivory:
```{r echo=FALSE}
below_plot <- june18_dat %>% 
  group_by(Plot, Site) %>% 
  summarize(mean = list(mean_se(below_prop))) %>% 
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = Plot)) +
  bar_plot +
  error_bars
  
below_plot
ggsave("plots/below_plot.png", width = 10, height = 7)
```

* below-ground herbivory basically only happens in Arid


Adding above-ground herbivory frequency to proportion dead model
```{r eval=FALSE, include=FALSE}
prop_mod_above <- update(prop_mod0, ~ Site + above_prop + (1|Site/Block))
#did this work? not sure why cnd(abv_prp) is a numeric value and not just a "+" like it usually is
model.sel(list(prop_mod0, prop_mod_above))
```

### Modelling Above-Ground Herbivory

Optimal fixed effects
```{r include=FALSE}
above_mod1 <- glmmTMB((herb_above/total) ~ Plot + Site + (1|Site/Block),
                      ziformula = ~ 0, family = binomial(),
                      data = june18_dat, weights = total)

above_mod2 <- update(above_mod1, ~ Site + (1|Site/Block))
above_mod3 <- update(above_mod1, ~ Plot + (1|Site/Block))
above_mod4 <- update(above_mod1, ~ (1|Site/Block))

model.sel(above_mod1, above_mod2, above_mod3, above_mod4)
```
* Plot-only model is best

Test ZI
```{r include=FALSE}
above_modZI <- update(above_mod3, ziformula = ~ 1)

model.sel(above_mod3, above_modZI)

above_mod2 <- update(above_modZI, ~ Plot + Site + (1|Site/Block))
above_mod3 <- update(above_modZI, ~ Site + (1|Site/Block))
above_mod4 <- update(above_modZI, ~ (1|Site/Block))

model.sel(above_modZI, above_mod2, above_mod3, above_mod4)
```
* ZI improves fit

```{r include=FALSE}
above_table <- model.sel(above_modZI, above_mod2, above_mod3, above_mod4) %>%
  gt() %>% 
    tab_header(title = "Model Comparison: Above-Ground Herbivory") %>%
    tab_spanner(label = md("*Fixed Effects*"), columns = 4:5) %>% 
    cols_label("cond(Plot)" = md("*Treatment*"), "cond(Site)" = md("*Climate*")) %>% 
    cols_hide(columns = c(1,2,3,7,9)) %>% 
    fmt_number(columns = vars(AICc, weight)) %>%
    fmt_missing(columns = 4:5, missing_text = "-")

gtsave(above_table, "plots/above_table.png")
```

```{r echo=FALSE}
above_table
```

DHARMa Diagnostics:
```{r echo=FALSE}
above_sim <- simulateResiduals(fittedModel = above_modZI, plot = F, n = 1000)
hist(above_sim)
testResiduals(above_sim, plot = T)
```
* uniformity, dispersion, and outlier tests all non-significant

Testing Effects
```{r echo=FALSE}
above_mod <- above_modZI

pairs(emmeans(above_mod, "Plot"))

june18_dat %>% 
  group_by(Plot) %>% 
  summarize(above_prop = mean(above_prop)) %>% 
  ggplot(aes(x = Plot, y = above_prop, fill = Plot)) +
    geom_bar(stat = "identity") +
    scale_fill_brewer(palette = "Dark2") +
    theme_bw()

june18_dat %>% 
  group_by(Plot) %>% 
  summarize(above_prop = mean(above_prop))
```
* O-WC and W-WC are significantly different
* note: contrasts are still on the cloglog scale

```{r eval=FALSE, include=FALSE}
ggplot(june18_dat, aes(x = Plot, y = above_prop)) +
  geom_boxplot() + theme_bw()
```

## Desiccation

```{r eval=FALSE, include=FALSE}
ggplot(june18_dat, aes(x = dess_YN)) +
  geom_histogram(binwidth = 1)
```

Dessication intensity (dead dess/total dess)
```{r eval=FALSE, include=FALSE}
june18_dat %>% 
  filter(dess_YN == 1) %>% 
  ggplot(aes(x = Site, y = dead_dess/(alive_dess + dead_dess), fill = Plot)) +
  geom_boxplot()
```


*dessication only happens in Arid and Interm O
*100% of plants with dessication are dead in Arid O, dessication less intense in W and WC
*however, arid has way higher prop dead so this may be expected even if dessication intensity is the same

Adjusting for overall proportion dead:
```{r eval=FALSE, include=FALSE}
june18_dat %>% 
  filter(dess_YN == 1) %>% 
  ggplot(aes(x = Site, y = (dead_dess/prop_dead)/(alive_dess + dead_dess), fill = Plot)) +
  geom_boxplot()
```

* effect reverses - Intermediate plots have a much higher proportion of death among dessicated seedlings

alternate measure of dessication intensity: what % of dead plants have dessication?
```{r eval=FALSE, include=FALSE}
june18_dat %>% 
  filter(dead_dess != 0) %>% 
  ggplot(aes(x = Site, y = (dead_dess/dead), fill = Plot)) +
  geom_boxplot()
```

* not super interesting, pretty similar for all plots with dead dessication

# Time to bring in ungulate data!
```{r eval=FALSE, include=FALSE}
herb_dat <- read.csv("data_raw/2018_herbivore_dung_data_herbivore_activity_proxy.csv")
View(herb_dat)
str(herb_dat)
```

```{r eval=FALSE, include=FALSE}
herb_dat <- herb_dat %>% 
  rename(survey_period = 1, Plot = 4, RE = 5) %>% 
  filter(survey_period == "EARLY SUMMER")

herb_dat$Plot <- recode(herb_dat$Plot, "OPEN" = "WC", "PARTIAL" = "W", "TOTAL" = "O")

ungulate_plot <- herb_dat %>% 
                  gather(ungulate_type, abundance, ALL_WILDLIFE:ALL_COW) %>% 
                  ggplot(aes(x = Plot, y = abundance, fill = ungulate_type)) +
                    geom_boxplot() + theme_bw() + scale_fill_brewer(palette = "Dark2")
ungulate_plot
ggsave("plots/ungulate_plot.png", width = 10, height = 7)
```

* looks like exclosures are working really well!
* seems like adding cattle increases ungulate presence much more than adding wildlife
