---
title: "Parsons_et_al_2021_analyses"
author: "John Parsons"
date: "`r Sys.Date()`"
output:
  html_document: default
---

### Load Required Packages
```{r include=FALSE}
#install.packages(c("cowplot", "DHARMa", "dplyr", "emmeans", "ggsignif", "glmmTMB", "gt", "installr", "lubridate", "MuMIn", "plotrix", "RColorBrewer", "tidyverse", "webshot"))

library(tidyverse) #cite ggplot, dplyr, and readr separately
group_by <- dplyr::group_by
summarize <- dplyr::summarise
select <- dplyr::select
recode <- dplyr::recode
rename <- dplyr::rename
library(lubridate) #date manipulation
library(RColorBrewer) #plot colors
library(MuMIn) #model.sel, dredge
library(glmmTMB) #GLMMs
library(DHARMa) #model diagnostics
library(emmeans) #effects testing
library(installr)
#install.pandoc()
#remotes::install_github("rstudio/gt")
library(gt) #table outputs
#webshot::install_phantomjs() 
library(webshot) #saving gt tables
library(plotrix)
library(cowplot)
library(ggsignif)

#sessionInfo()
#citation("emmeans")
#updateR()
```

### Data Tidying/Transformations
```{r include=FALSE}
#read in data
june18_dat <- read.csv("data_raw/SeedlingTransectDataRawSummer18.csv",
                       header = TRUE, na.strings = "")
str(june18_dat)
#View(june18_dat)

#remove blank rows and columns
june18_dat <- june18_dat %>% 
  select(-17, -18, -19) %>% 
  slice(3:nrow(june18_dat))

#move first row to column names and remove first row
colnames(june18_dat) <- as.matrix(june18_dat[1,])
june18_dat <- slice(june18_dat, 2:nrow(june18_dat))

#get rid of unused levels
june18_dat <- droplevels(june18_dat)
june18_dat$Site <- recode(june18_dat$Site, "Intermediate " = "Intermediate", "Mesic " = "Mesic")
june18_dat$Plot <- recode(june18_dat$Plot, "1" = "O", "2" = "W", "3" = "WC")

#fill out all rows of first three columns
june18_dat <- fill(june18_dat, 1:3, .direction = "down")

#fix names
june18_dat <- june18_dat %>% 
  rename(seedlings = 8,
                after_1st_yr = 9,
                old_seedlings = 10,
                alive_dess = 13,
                dead_dess = 14,
                herb_above = 15,
                herb_below = 16)

#convert factors to numeric
june18_dat <- june18_dat %>% 
  mutate_at(c("seedlings", "after_1st_yr", "old_seedlings", "dead", "clump", "alive_dess", "dead_dess", "herb_above", "herb_below"), as.character) %>% 
  mutate_at(c("seedlings", "after_1st_yr", "old_seedlings", "dead", "clump", "alive_dess", "dead_dess", "herb_above", "herb_below"), as.numeric)

#replace na's with 0's
june18_dat[is.na(june18_dat)] <- 0

#sum across transects
june18_dat <- june18_dat %>% 
  dplyr::group_by(Year, Month, Site, Block, Plot) %>% 
  summarise(seedlings = sum(seedlings), after_1st_yr = sum(after_1st_yr), old_seedlings = sum(old_seedlings), dead = sum(dead), clump = sum(clump), alive_dess = sum(alive_dess), dead_dess = sum(dead_dess), herb_above = sum(herb_above), herb_below = sum(herb_below))

#new column for large herbivore presence (W or WC)
june18_dat <- june18_dat %>% 
  mutate(grazed_YN = if_else(Plot == "O", 0, 1))
june18_dat$grazed_YN <- as.factor(june18_dat$grazed_YN)

#new columns for total seedlings, alive seedlings and proportion dead
june18_dat <- june18_dat %>% 
  mutate(total = seedlings + after_1st_yr + old_seedlings) %>% 
  mutate(alive = total - dead) %>% 
  mutate(prop_dead = (dead/total))

#new column for dessication occurrence
june18_dat <- june18_dat %>% 
  mutate(dess_YN = if_else(alive_dess != 0, 1, if_else(dead_dess != 0, 1, 0)))

#new columns for above-ground, below-ground, and overall herbivory occurrence, and for proportion of seedlings with above- or below-ground herbivory
june18_dat <- june18_dat %>% 
  mutate(above_YN = if_else(herb_above == 0, 0, 1)) %>%
  mutate(below_YN = if_else(herb_below == 0, 0, 1)) %>% 
  mutate(both_herb = if_else((herb_below == 1 | herb_above == 1), 1, 0)) %>% 
  mutate(herb_YN = if_else(above_YN == 1, 1, if_else(below_YN == 1, 1, 0))) %>% 
  mutate(above_prop = herb_above/total) %>% 
  mutate(below_prop = herb_below/total)
june18_dat$above_YN <- as.factor(june18_dat$above_YN)
june18_dat$below_YN <- as.factor(june18_dat$below_YN)
june18_dat$both_herb <- as.factor(june18_dat$both_herb)
june18_dat$herb_YN <- as.factor(june18_dat$herb_YN)
```

## Total Seedling Abundance

### Exploratory Visualizations
```{r echo=FALSE}
ggplot(june18_dat, aes(x = total))+
  geom_histogram(binwidth = 10)

ggplot(june18_dat, aes(x = total)) +
  stat_ecdf(geom = "step")
```

* these visualizations correspond to seedling establishment (includes both alive and dead seedlings)
* see next section for visualizations of living seedlings only (seedling survival)

Total seedling abundance by site and plot, with significance codes (Figure 2):
```{r echo=FALSE}
total_plot_sig <- june18_dat %>%
  dplyr::group_by(Site, Plot) %>% 
  dplyr::summarize(mean = list(mean_se(total))) %>%
  unnest(mean) %>% 
  mutate(sig = if_else(Plot == "O", "a", if_else(Plot == "W", "b", "c"))) %>% 
  ggplot(aes(x = Site, y = y, fill = Plot)) +
    geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
    geom_text(aes(label = sig), position = position_dodge(width = 0.9),
                                size = 5, vjust = -0.5, hjust = 1.8) +
    geom_errorbar(aes(ymax = ymax, ymin = ymin),
                  position = position_dodge(width = 0.9),
                  width = 0.2) +
    labs(x = "Climate Level", 
         y = "Average Number of Seedlings per Plot") +
    scale_fill_brewer("Grazing Treatment",
                      labels = c("Exclsoure", "Wildlife", "Open"),
                      palette = "Dark2") +
    theme_cowplot() +
  ggsave("plots/total_plot_sig.png", width = 10, height = 7)

total_plot_sig
```

save settings for other charts
```{r include=FALSE}
bar_plot <- geom_bar(stat = "identity", position = position_dodge(width = 0.9))
error_bars <- geom_errorbar(aes(ymax = ymax, ymin = ymin),
                                position = position_dodge(width = 0.9),
                                width = 0.2)
```

### Modelling Total Seedling Abundance

Optimal Fixed Effects Structure:
```{r include=FALSE}
#no zeroes in summed count data (see above)
#start with truncated poisson distribution and full model:
total_mod <- glmmTMB(total ~ Site*Plot + (1|Site/Block), data = june18_dat, family = truncated_poisson)

total_dredge_table <- total_mod %>%
  dredge() %>% 
  gt() %>% 
    tab_header(title = "Model Comparison: Total Seedling Abundance") %>%
    tab_spanner(label = md("*Fixed Effects*"), columns = 3:5) %>% 
    cols_label("cond(Plot)" = "Treatment", 
               "cond(Site)" = "Climate",
               "cond(Plot:Site)" = "Treatment:Climate") %>% 
    cols_hide(columns = c(1,2,7,9,10)) %>% 
    fmt_number(columns = vars(AICc)) %>%
    fmt_missing(columns = 3:5, missing_text = "-")
gtsave(total_dredge_table, "plots/total_table.png")

total_dredge_table #Table S2
```
* Full model is best

DHARMa Diagnostics:
```{r echo=FALSE}
total_sim <- simulateResiduals(fittedModel = total_mod, plot = F, n = 1000)
hist(total_sim)
testResiduals(total_sim, plot = T)
```

*uniformity, dispersion, and outlier tests all non-significant

Test other distributions
```{r eval=FALSE, include=FALSE}
fam_list <- list(family = alist(
    truncpois = truncated_poisson,
    genpois = genpois,
    poisson = poisson,
    nbinom1 = nbinom1,
    nbinom2 = nbinom2
    ))

dredge(total_mod, varying = fam_list)
#truncated poisson only marginally better than regular poisson

total_mod_pois <- update(total_mod, family = poisson)

total_pois_sim <- simulateResiduals(fittedModel = total_mod_pois, plot = F, n = 1000)
hist(total_pois_sim)
testResiduals(total_pois_sim, plot = T)
#meets assumptions well

model.sel(list(total_mod, total_mod_pois))
```

Testing Effects
```{r echo=FALSE}
pairs(emmeans(total_mod, ~ Plot * Site))
      
emmeans(total_mod, pairwise ~ Site)
#all non-sig
emmeans(total_mod, pairwise ~ Plot)
#all significant

emmip(total_mod, Plot ~ Site)
#subsetting by Plot:
emmeans(total_mod, pairwise ~ Site | Plot)
#all Site contrasts non-significant 

emmip(total_mod, Site ~ Plot)
#subsetting by Site:
emmeans(total_mod, pairwise ~ Plot | Site)
#all Plot contrasts significant
```

* Climate, grazing treatment, and their interaction were all included as fixed effects in the model of best fit. Arid, intermediate, and mesic plots had an average of 80, 111, and 120 seedlings. There were no significant differences in seedling abundance between climates, either within each grazing treatment or when averaged across the three treatments. Across climates, exclosure plots had an average of 162 seedlings, more than both wildlife plots (93, p < 0.0001) and wildlife/cattle plots (46, p < 0.0001). Contrasts were also significant for all treatment pairs within climate levels (Table 1).

## Seedling Mortality

### Exploratory Visualizations

```{r echo=FALSE}
ggplot(june18_dat, aes(x = alive/total)) + 
  geom_histogram(binwidth = 0.1)
```

* lots of plots with >90% alive

Proportion dead by plot and site (Figure 3):
```{r include=FALSE}
prop_plot <- june18_dat %>% 
  group_by(Site, Plot) %>% 
  summarize(mean = list(mean_se(prop_dead))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = Plot)) +
    bar_plot +
    error_bars +
    geom_signif(annotations = c("p < 0.005", "p < 0.001", "p = 0.07"),
                y_position = c(1.05, 1.15, 0.4), 
                xmin=c(1,1,2), xmax=c(2,3,3), tip_length = 0) +
    labs(x = "Climate Level", 
         y = "Proportion of Seedlings Dead") +
    scale_y_continuous(breaks = c(0.2,0.4,0.6,0.8,1)) +
    scale_fill_brewer("Grazing Treatment", labels = c("Exclosure", "Wildlife", "Open"),
                      palette = "Dark2") +
    theme_cowplot() +
ggsave("plots/prop_plot.png", width = 10, height = 7)
```

```{r echo=FALSE}
prop_plot
```
* arid has way higher proportion of dead seedlings than other climate levels
* very similar across grazing treatments

### Modelling Proportion Dead

```{r include=FALSE}
#start with binomial distribution 
prop_mod1 <- glmmTMB(cbind(dead, alive) ~ Site + Plot + (1|Site/Block),
                     ziformula = ~ 0, data = june18_dat,
                     family = binomial())
```

Optimal Fixed Effects Structure
```{r include=FALSE}
prop_mod2 <- update(prop_mod1, ~ Plot + (1|Site/Block))
prop_mod3 <- update(prop_mod1, ~ Site + (1|Site/Block))
prop_mod4 <- update(prop_mod1, ~(1|Site/Block))

model.sel(prop_mod1, prop_mod2, prop_mod3, prop_mod4)
#full model is best
```

Optimal ZI Formula?
```{r include=FALSE}
prop_modZI <- update(prop_mod1, ziformula = ~1)

model.sel(list(prop_mod1, prop_modZI))
#ZI is better

prop_mod2 <- update(prop_modZI, ~ Plot + (1|Site/Block))
prop_mod3 <- update(prop_modZI, ~ Site + (1|Site/Block))
#fails to converge
prop_mod4 <- update(prop_modZI, ~(1|Site/Block))

prop_table <- model.sel(prop_modZI, prop_mod2, prop_mod4) %>%
  gt() %>% 
    tab_header(title = "Model Comparison: Seedling Mortality") %>%
    tab_spanner(label = md("*Fixed Effects*"), columns = 4:5) %>% 
    cols_label("cond(Plot)" = md("Treatment"), "cond(Site)" = md("Climate Level")) %>% 
    cols_hide(columns = c(1,2,3,6,7,9,10)) %>% 
    fmt_number(columns = vars(AICc)) %>%
    fmt_missing(columns = 4:5, missing_text = "-")
gtsave(prop_table, "plots/prop_table.png") #Table S3

prop_mod <- prop_modZI
```

```{r echo=FALSE}
prop_table
```

DHARMa Diagnostics:
```{r echo=FALSE}
prop_dead_sim <- simulateResiduals(fittedModel = prop_mod, plot = F, n = 1000)
hist(prop_dead_sim)
testResiduals(prop_dead_sim, plot = T)
```
* uniformity, dispersion, and outlier tests all non-significant

Testing Effects
```{r echo=FALSE}
ggplot(june18_dat, aes(x = Plot, y = (alive/total), fill = Site)) +
  geom_boxplot() + 
  theme_bw()
#more variation between sites than plots, so group by site and then get pairwise contrasts between plots?

pairs(emmeans(prop_mod, "Plot"))
# O-W and O-WC are significant

pairs(emmeans(prop_mod, "Site"))
#Arid-Interm and Arid-Mesic are significant

#subsetting by climate level:
emmeans(prop_mod, pairwise ~ Plot | Site)
```

* The best-fit model for seedling mortality included both climate level and grazing treatment (Table 1). Arid plots had 80.15% mortality, more than both Mesic plots (0.53%, p < 0.0001) and Intermediate plots (10.43%, p < 0.001). Intermediate plots did not have significantly higher mortality than Mesic plots (p = 0.07). Across climate levels, exclosure plots (33.46%) and wildlife/cattle plots (29.33%) did not significantly differ in their mortality rates (p = 0.1774). 28.32% of seedlings died in wildlife plots,  more than exclosure plots (p < 0.0005) and less than wildlife/cattle plots (p < 0.05).

#### Arid Mortality Model
```{r}
#subset dataset
arid_dat <- june18_dat %>% 
  filter(Site == "Arid")
#start with binomial distribution 
arid_mod1 <- glmmTMB(cbind(dead, alive) ~ Plot + (1|Site/Block),
                     ziformula = ~ 0, data = arid_dat,
                     family = binomial())

arid_mod2 <- update(arid_mod1, ~ (1|Site/Block))
arid_modZI <- update(arid_mod1, ziformula = ~1)
arid_modZI2 <- update(arid_modZI, ~ (1|Site/Block))

model.sel(arid_mod1, arid_mod2, arid_modZI, arid_modZI2)
#non-ZI full model is best

arid_mod <- arid_mod1

arid_dead_sim <- simulateResiduals(fittedModel = arid_mod, plot = F, n = 1000)
hist(arid_dead_sim)
testResiduals(prop_dead_sim, plot = T)

pairs(emmeans(arid_mod, "Plot"))
```

## Living Seedling Abundance

### Exploratory Visualizations
```{r}
ggplot(june18_dat, aes(x = alive))+
  geom_histogram(binwidth = 5)
#looks like negative binomial?

ggplot(june18_dat, aes(x = alive)) +
  stat_ecdf(geom = "step")
```

Living seedling abundance by site and plot (Figure 4):
```{r echo=FALSE}
alive_plot <- june18_dat %>% 
  dplyr::group_by(Site, Plot) %>% 
  dplyr::summarize(mean = list(mean_se(alive))) %>%
  unnest(mean) %>%
  add_column(sig = c("a", "b", "a", "a", "b", "c", "a", "b", "c")) %>% 
  ggplot(aes(x = Site, y = y, fill = Plot)) +
    bar_plot +
    error_bars +
    geom_text(aes(label = sig), position = position_dodge(width = 0.9),
              size = 5, vjust = -0.5, hjust = 1.8) +
    labs(x = "Climate Level", 
         y = "Average Number of Live Seedlings per Plot") +
    scale_fill_brewer("Grazing Treatment", labels = c("Exclosure", "Wildlife", "Open"),
                      palette = "Dark2") +
  theme_cowplot() +
  ggsave("plots/alive_plot.png", width = 10)
alive_plot
```

* all three sites are different - unlike total seedlings
* arid vs mesic affects survival, not establishment?

### Modeling Living Seedling Abundance
```{r include=FALSE}
#starting with poisson:
alive_mod1 <- glmmTMB(alive ~ Site*Plot + (1|Site/Block), 
                      data = june18_dat, family = poisson(), ziformula = ~ 0)
```

Optimal Fixed Effects and ZI Formula
```{r include=FALSE}
dredge(alive_mod1)
#Full model is best

alive_mod2 <- update(alive_mod1, ziformula = ~ 1)

model.sel(alive_mod1, alive_mod2)
#ZI ~ 1 is better than no ZI

alive_mod <- alive_mod2

alive_table <- dredge(alive_mod) %>% 
  gt() %>% 
    tab_header(title = "Model Comparison: Living Seedling Abundance") %>%
    tab_spanner(label = md("*Fixed Effects*"),
                              columns = 4:6) %>% 
    cols_label("cond(Plot)" = "Treatment", 
                             "cond(Site)" = "Climate", 
                             "cond(Plot:Site)" = "Treatment:Climate") %>% 
    cols_hide(columns = c(1:3,8,10,11)) %>% 
    fmt_number(columns = vars(AICc)) %>%
    fmt_missing(columns = 4:6, missing_text = "-")
gtsave(alive_table, "plots/alive_table.png")
```

```{r echo=FALSE}
alive_table #Table S4
```

DHARMa Diagnostics:
```{r echo=FALSE}
alive_sim <- simulateResiduals(fittedModel = alive_mod, plot = F, n = 1000)
hist(alive_sim)
testResiduals(alive_sim, plot = T)
```

*uniformity, dispersion, and outlier tests all non-significant

Testing Effects
```{r echo=FALSE}
pairs(emmeans(alive_mod, "Plot"))

pairs(emmeans(alive_mod, ~ Plot | Site))

pairs(emmeans(alive_mod, "Site"))

pairs(emmeans(alive_mod, ~ Site | Plot))
```

* The best-fit model of living seedlings included grazing treatment, but not climate level. Wildlife/cattle plots had 35 living seedlings on average, less than exclosure plots (135, p < 0.005) and wildlife plots (67, p < 0.05). Exclosure and wildlife plots did not differ significantly (p = 0.3970).

## Above-Ground Herbivory

### Herbivory visualizations
```{r eval=FALSE, include=FALSE}
ggplot(june18_dat, aes(x=herb_above)) +
  geom_histogram(binwidth = 1)

ggplot(june18_dat, aes(x=above_prop)) +
  geom_histogram()
```

Proportion of seedlings with above-ground herbivory (Figure 5):
```{r echo=FALSE}
above_plot <- june18_dat %>% 
  group_by(Plot, Site) %>% 
  summarize(mean = list(mean_se(above_prop))) %>% 
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = Plot)) +
    bar_plot +
    error_bars +
    labs(x = "Climate Level", 
         y = "Herbivory Occurrence") +
    scale_fill_brewer("Grazing Treatment", labels = c("Exclosure", "Wildlife", "Open"),
                      palette = "Dark2") +
    theme_cowplot() +
    ggsave("plots/above_plot.png", width = 10, height = 7)
```

```{r}
above_plot
```

* pretty intuitive, addition of cattle clearly increases above-ground herbivory, especially in mesic

Proportion of seedlings with below-ground herbivory (Figure S2):
```{r echo=FALSE}
below_plot <- june18_dat %>% 
  group_by(Plot, Site) %>% 
  summarize(mean = list(mean_se(below_prop))) %>% 
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = Plot)) +
    bar_plot +
    error_bars +
    labs(x = "Climate Level", 
         y = "Herbivory Occurrence") +
    scale_fill_brewer("Grazing Treatment", labels = c("Exclosure", "Wildlife", "Open"),
                      palette = "Dark2") +
    theme_cowplot() +
    ggsave("plots/below_plot.png", width = 10, height = 7)
```

```{r}
below_plot
```

* below-ground herbivory basically only happens in Arid

### Modelling Above-Ground Herbivory

Optimal fixed effects
```{r include=FALSE}
above_mod1 <- glmmTMB(cbind(herb_above,(total-herb_above)) ~ Plot + Site + (1|Site/Block),
                      ziformula = ~ 0, family = binomial(),
                      data = june18_dat)

above_mod2 <- update(above_mod1, ~ Site + (1|Site/Block))
above_mod3 <- update(above_mod1, ~ Plot + (1|Site/Block))
above_mod4 <- update(above_mod1, ~ (1|Site/Block))

model.sel(above_mod1, above_mod2, above_mod3, above_mod4)
```
* Plot-only model is best

Test ZI
```{r include=FALSE}
above_modZI <- update(above_mod3, ziformula = ~ 1)

model.sel(above_mod3, above_modZI)

above_mod2 <- update(above_modZI, ~ Plot + Site + (1|Site/Block))
above_mod3 <- update(above_modZI, ~ Site + (1|Site/Block))
above_mod4 <- update(above_modZI, ~ (1|Site/Block))

model.sel(above_modZI, above_mod2, above_mod3, above_mod4)
```
* ZI improves fit

```{r include=FALSE}
above_table <- model.sel(above_modZI, above_mod2, above_mod3, above_mod4) %>%
  gt() %>% 
    tab_header(title = "Model Comparison: Above-Ground Herbivory") %>%
    tab_spanner(label = md("*Fixed Effects*"), columns = 4:5) %>% 
    cols_label("cond(Plot)" = md("*Treatment*"),
               "cond(Site)" = md("*Climate Level*")) %>% 
    cols_hide(columns = c(1,2,3,6,8,9)) %>% 
    fmt_number(columns = vars(delta, weight), decimals = 3) %>%
    fmt_missing(columns = 4:5, missing_text = "-")
gtsave(above_table, "plots/above_table.png")
```

```{r echo=FALSE}
above_table  #Table S5
```

DHARMa Diagnostics:
```{r echo=FALSE}
above_sim <- simulateResiduals(fittedModel = above_modZI, plot = F, n = 1000)
hist(above_sim)
testResiduals(above_sim, plot = T)
```
* uniformity, dispersion, and outlier tests all non-significant

Testing Effects
```{r echo=FALSE}
above_mod <- above_modZI

pairs(emmeans(above_mod, "Plot"))

june18_dat %>% 
  group_by(Plot) %>% 
  summarize(above_prop = mean(above_prop)) %>% 
  ggplot(aes(x = Plot, y = above_prop)) +
    geom_bar(stat = "identity")
```
* O-WC and W-WC are significantly different
* note: contrasts are still on the cloglog scale

# Summary Table of all Response Variables (Table S1)
```{r include=FALSE}
summary_table_mean <- june18_dat %>% 
  group_by(Plot, Site) %>% 
  summarize_at(vars(total, alive, prop_dead, above_prop), funs(mean)) %>% 
  ungroup() %>%
  rename("Total seedlings" = total, "Living seedlings" = alive,
         "Proportion dead" = prop_dead,
         "Proportion with aboveground herbivory" = above_prop) %>% 
  t() %>% 
  as.data.frame() %>% 
  rownames_to_column() %>%
  slice(3:6)

summary_table_se <- june18_dat %>% 
  group_by(Plot, Site) %>% 
  summarize_at(vars(total, alive, prop_dead, above_prop),
               funs(std.error(.))) %>% 
  ungroup() %>%
  rename("Total seedlings" = total, "Living seedlings" = alive,
         "Proportion dead" = prop_dead,
         "Proportion with aboveground herbivory" = above_prop) %>%
  t() %>% 
  as.data.frame() %>% 
  rownames_to_column() %>% 
  slice(3:6)

summary <- bind_cols(summary_table_mean, summary_table_se)

write.csv(summary, "summary")
summary <- read.csv("summary")
str(summary)

summary_table <- summary %>%
  rename("rowname" = rowname...1) %>% 
  select(-1) %>% 
  select(-11) %>% 
  gt() %>%
    fmt_number(columns = 2:19, decimals = 3) %>% 
    cols_merge_uncert(2, 11, autohide = T) %>% 
    cols_merge_uncert(3, 12, autohide = T) %>% 
    cols_merge_uncert(4, 13, autohide = T) %>% 
    cols_merge_uncert(5, 14, autohide = T) %>% 
    cols_merge_uncert(6, 15, autohide = T) %>% 
    cols_merge_uncert(7, 16, autohide = T) %>% 
    cols_merge_uncert(8, 17, autohide = T) %>% 
    cols_merge_uncert(9, 18, autohide = T) %>%
    cols_merge_uncert(10, 19, autohide = T) %>% 
    #tab_header(title = "Summary of Results") %>%
    tab_spanner(label = md("**Arid**"), columns = c(2,5,8)) %>% 
    tab_spanner(label = md("**Intermediate**"), columns = c(3,6,9)) %>% 
    tab_spanner(label = md("**Mesic**"), columns = c(4,7,10)) %>% 
    tab_stubhead(label = md("*Response variable*")) %>% 
    cols_label(V1...2 = "X", V4...5 = "W", V7...8 = "WC",
               V2...3 = "X", V5...6 = "W", V8...9 = "WC",
               V3...4 = "X", V6...7 = "W", V9...10 = "WC")
summary_table
gtsave(summary_table, "plots/summary_table.png")
```

```{r echo=FALSE}
summary_table
```

## Desiccation

```{r eval=FALSE, include=FALSE}
ggplot(june18_dat, aes(x = dess_YN)) +
  geom_histogram(binwidth = 1)
```

Dessication prevalence 
```{r eval=FALSE, include=FALSE}
june18_dat %>% 
  group_by(Site, Plot) %>% 
  summarize(mean = list(mean_se((alive_dess + dead_dess)/total))) %>%
  unnest(mean) %>% 
  ggplot(aes(x = Site, y = y, fill = Plot)) +
    bar_plot +
    error_bars +
    labs(x = "Climate Level", 
         y = "Dessication Prevalance") +
    scale_fill_brewer("Grazing Treatment", labels = c("Exclosure", "Wildlife", "Open"),
                      palette = "Dark2") +
    theme_cowplot() +
ggsave("plots/dess_plot.png", width = 10, height = 7) #Figure S2
``` 